Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-23 paper.qmd
sharing the link

This command utilizes the `default.nix` file to build the exact computational
environment required to compile the manuscript. To ensure continuous
reproducibility, the paper is also automatically re-compiled via GitHub Actions
on every push to the repository, using the same Nix environment.

>>>>

The `default.nix` file defines the exact computational environment required to
compile the manuscript, ensuring full reproducibility of the build process. To
guarantee the reproducibility of the manuscript, it is automatically
recompiled via GitHub Actions upon each commit, using the same Nix environment.
An HTML version is additionally deployed to GitHub Pages, providing an
accessible format for viewing on smaller devices at this
[link](https://b-rodrigues.github.io/rix_paper/)^[[https://b-rodrigues.github.io/rix_paper/](https://b-rodrigues.github.io/rix_paper/)].
